First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration

### 2025-01-24 Notebook LaTEX/Proposal/presentation.tex
>w<, changes
>w<, fixes

\documentclass[11pt]{beamer}
\usetheme{Madrid}
\usepackage[utf8]{inputenc}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\DeclareMathOperator{\argmin}{argmin}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{subcaption}
\graphicspath{{.}}

\author{Generic Name}
\title{Title for Super Fancy Stuff}
% Informe o seu email de contato no comando a seguir
% Por exemplo, alcebiades.col@ufes.br
\newcommand{\email}{lalala@lala.la}
\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
%\logo{}
\institute[]{Some Super Fancy Institution}
\date{\today}
\subject{Subject Title }

@@

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{ToC}
    \tableofcontents
\end{frame}

% \section{This is the First Section}
%     \subsection{Taxonomy of Proximal type of Methods}
%         \begin{frame}{Frame Title}

%             \begin{block}{Formula Presented in Block}
%                 \begin{align}
%                     \min_{x} g(x) + h(x)
%                 \end{align}    
%             \end{block}

%             \begin{itemize}
%                 \item [1.]Throughout this presentation, we assume the objective of a function $f$ is the sum of 2 functions.
%                 \item [2.]We are interested in the paper: FISTA (Fast Iterative-Shrinkage Algorithm) by Beck and Teboulle \cite{paper:FISTA}. 
%                 \pause 
%                 \item [1.] When $h = \delta_Q$ with $Q$ closed and convex with $Q\subseteq \text{ri}\circ \text{dom}(g)$, we use projected subgradient. 
%                 \item [2.] When $g$ is \textbf{\emph{strongly smooth}} and $h$ is \textbf{closed convex proper} whose proximal oracle is easy to compute, we consider the use of FISTA. 
%             \end{itemize}

%         \end{frame}

%     \subsection{The Proximal Operator}
%         \begin{frame}{Frame Title}
%             \begin{definition}[Definition of Something]
%                 Let $f$ be convex closed and proper, then the proximal operator parameterized by $\alpha > 0$ is a non-expansive mapping defined as: 
%                 \begin{align*}
%                     \text{prox}_{f, \alpha}(x) := 
%                     \arg\min_{y}\left\lbrace
%                         f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2
%                     \right\rbrace. 
%                 \end{align*}
%             \end{definition}  
%             \begin{remark}
%                 When $f$ is convex, closed, and proper, 
%             \end{remark}
%         \end{frame}

%         \begin{frame}{Prox is the Resolvant of Subgradient}
%             \begin{lemma}[The Lemma]\label{lemma:prox_alternative_form}
%                 When the function $f$ is convex closed and proper, the $\text{prox}_{\alpha, f}$ can be viewed as the following operator $(I + \alpha \partial f)^{-1}$. 
%             \end{lemma}
%             \begin{proof}
%                 Minimizer satisfies zero subgradient condition, 
%                 {\scriptsize
%                 \begin{align*}
%                     \mathbf 0 &\in \partial
%                     \left[
%                         \left.
%                             f(y) + \frac{1}{2\alpha} \Vert y - x\Vert^2 
%                         \right| y
%                     \right](y^+)
%                     \\
%                     \mathbf 0 &\in \partial f(y^+) + \frac{1}{\alpha}(y^+ - x)
%                     \\
%                     \frac{x}{\alpha} &\in 
%                     (\partial f + \alpha^{-1}I)(y^+)
%                     \\
%                     x &\in 
%                     (\alpha \partial f + I)(y^+)
%                     \\
%                     y &\in (\alpha\partial f+ I)^{-1}(x).
%                 \end{align*}
%                 }
%             \end{proof}
%         \end{frame}

%     \subsection{Strong Smoothness}
%         \begin{frame}{Equivalence of Strong Smoothness and Lipschitz Gradient}
%             \begin{theorem}[Lipschitz Gradient Equivalence under Convexity]
%                 Suppose $g$ is differentiable on the entire of $\mathbb E$. It is closed convex proper. It is strongly smooth with parameter $\alpha$ if and only if the gradient $\nabla g$ is globally Lipschitz continuous with a parameter of $\alpha$ and $g$ is closed and convex. 
%                 \begin{align*}
%                     \Vert \nabla g(x) -\nabla g(y)\Vert \le 
%                     \alpha 
%                     \Vert x - y \Vert\quad \forall x, y\in \mathbb E
%                 \end{align*}
%             \end{theorem}
%             \begin{proof}
%                 Using line integral, we can prove Lipschitz gradient implies strong smoothness without convexity. The converse requires convexity and applying generalized Cauchy Inequality to (iv) in Theorem 5.8 for Beck's textbook \cite{book:first_order_opt}. 
%             \end{proof}

%         \end{frame}
%     \subsection{A Major Assumption}    
%         \begin{frame}{A Major Assumption}
%             \begin{assumption}[Convex Smooth Nonsmooth with Bounded Minimizers]\label{assumption:1}
%                 We will assume that $g:\mathbb E\mapsto \mathbb R$ is \textbf{strongly smooth} with constant $L_g$ and $h:\mathbb E \mapsto \bar{\mathbb R}$ \textbf{is closed convex and proper}. We define $f := g + h$ to be the summed function and $\text{ri}\circ \text{dom}(g) \cap \text{ri}\circ \text{dom}(h) \neq \emptyset$. We also assume that a set of minimizers exists for the function $f$ and that the set is bounded. Denote the minimizer using $\bar x$. 
%             \end{assumption}
%         \end{frame}

% \section{A New Fancy Section}
%     \subsection{A Fancy Subsetction for Algorithm}
%         \begin{frame}{The Accelerated Proximal Gradient Method}
%             \begin{block}{Momentum Template Method}
%                 \begin{algorithm}[H]
%                     \begin{algorithmic}[1]
%                         \STATE{\textbf{Input:} $x^{(0)}, x^{(-1)}, L, h, g$; 2 initial guesses and stepsize L}
%                         \STATE{$y^{(0)} = x^{(0)} + \theta_k (x^{(0)} - x^{(-1)})$}
%                         \FOR{$k = 1, \cdots, N$}
%                             \STATE{$x^{(k)} = \text{prox}_{h, L^{-1}}(y^{(k)} + L^{-1}\nabla g(y^{(k)})) =: \mathcal P_{L^{-1}}^{g, h}(y^{(k)})$}
%                             \STATE{$y^{(k + 1)} = x^{(k)} + \theta_k(x^{(k)} - x^{(k - 1)})$}
%                         \ENDFOR
%                     \end{algorithmic}
%                     \caption{Template Proximal Gradient Method With Momentum}\label{alg:fista_template}
%                 \end{algorithm}
%             \end{block}
%         \end{frame}

% \section{Numerical Experiments}
%     \input{Sections/sectionfile.tex}

\section{References}
    \begin{frame}{References}

        \bibliography{references/proposal.bib}
    \end{frame}

>>>>

\documentclass[11pt]{beamer}

\usetheme{Madrid}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{subcaption}
\graphicspath{{.}}
\input{presets/wang/custom_commands.tex}

\author{Hongda Li}
\title[Thesis Proposal Talk]{First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration}
\newcommand{\email}{lalala@lala.la}
\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}
%\logo{}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date{\today}
\subject{Nesterov's acceleration and its applications}

@@

\begin{frame}
    \titlepage
\end{frame}
\begin{frame}{Overview}
    This talks will be based on the content of our draft paper and selected content of the Catalyst Meta Acceleration Framework. 
    Our preprint: 
    \begin{enumerate}
        \item X. Wang and H. Li, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
    \end{enumerate}
    Catalyst Meta Acceleration:  
    \begin{enumerate}
        \item H. Lin, J. Mairal and Z. Harchaoui, \textit{A universal catalyst for first-order optimization}, in NISP, vol. 28, (2015). 
        \item \underline{\hspace{4em}}, \textit{Catalyst acceleration for first-order convex optimization: from theory to practice}, JMLR, 18 (2018), pp. 1–54.
    \end{enumerate}
\end{frame}
\begin{frame}{ToC}
    \tableofcontents
\end{frame}

\section{Introduction}
    \subsection{Notations and preliminaries}
        \begin{frame}{Notations and preliminaries}
            Throughout this talk, let $\RR^n$ be the ambient space equiped with Euclidean inner product and norm. 
            We consider 
            \begin{align}\label{eqn:additive-comp-obj}
                \min_{x \in \RR^n} \left\lbrace
                    F(x):= f(x) + g(x)
                \right\rbrace.
            \end{align}
            Unless specified, assume: 
            \begin{enumerate}
                \item $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex, 
                \item $g:\RR^n \rightarrow \overline \RR$ is closed convex proper. 
            \end{enumerate}
        \end{frame}
        \begin{frame}{Our works on R-WAPG}

        \end{frame}
        \begin{frame}{Introduction to Catalyst Acceleration}

        \end{frame}
\section{Content of the draft paper}

    \subsection{Direction of future works}

\section{Selected contents from Catalyst Meta Accelerations}
    \subsection{Direction of future works}

\section{References}
    \begin{frame}{Citation examples}
        Citation examples \cite{chambolle_convergence_2015}
    \end{frame}
    \begin{frame}[allowframebreaks]{References}
        % \bibliographystyle{apalike}
        \bibliography{references/proposal.bib}
    \end{frame}
